Still Missing a Cool Title

### 2006-05-31 talk/dls2006/paper.tex
more bib tweaks

But RPython comes with automatic memory management, and this first
transformation step produces flow graphs that also assume automatic
memory management.  Generating C code directly from there produces a
fully leaking program, unless we link it with an external garbage
collector (GC) like the Boehm conservative GC \cite{Boehm}, which is a
viable option.

@@

We found in-process debugging sufficient and did not implement dumping
of any intermediate step to disk.  Figure 3 shows the control flow graph
obtained for a simple function -- this is a screenshot from our graph
viewer, used for debugging; basic block placement is performed by
[Graphviz].

>>>>

But RPython comes with automatic memory management, and this first
transformation step produces flow graphs that also assume automatic
memory management.  Generating C code directly from there produces a
fully leaking program, unless we link it with an external garbage
collector (GC) like the Boehm conservative GC \cite{Boehm}\cite{boehm-softw},
which is a viable option.

@@

We found in-process debugging sufficient and did not implement dumping
of any intermediate step to disk.  Figure 3 shows the control flow graph
obtained for a simple function -- this is a screenshot from our graph
viewer, used for debugging; basic block placement is performed by
Graphviz \cite{graphviz}.
